State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-07 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed parameter distribution caption

\caption{\parham{caption should be changed}Distribution of the parameters estimates over 100
realisations. Grey bars show distributions with wider basis functions ($\sigma_{\phi} = ?$) and blue bars show improved parameter distributions with narrower basis functions ($\sigma_{\phi} = ?$). \textbf{a.} The distribution of the synaptic time constant estimates (true parameter: $\zeta=100$). \textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameters estimates (true parameter: $\theta_0 = 10$). \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$). \textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}

>>>>

\caption{Distribution of the parameters estimates over 100
realisations. \textbf{a.} The distribution of the synaptic time constant estimates (true parameter: $\zeta=100$). \textbf{b.} The distribution of the central excitatory connectivity kernel basis function parameters estimates (true parameter: $\theta_0 = 10$). \textbf{c.} The distribution of the surround inhibition connectivity kernel basis function parameter estimates (true parameter: $\theta_1 = -8$). \textbf{d.} The distribution of the longer range excitatory connectivity kernel basis function parameter estimates (true parameter $\theta_3 = 0.5$).}
